---
title: "Mini-Project 02"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true
---

# Data Visualization Project 02

_revised version of mini-project 02 goes here_
---
title: "dataviz_mini-project_02"
author: "Sidney Ang"
date: "2025-06-12"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

# Data Visualization 

> Sidney Ang. 

## Mini-Project 2

Description of your project goes here. 
You can include a motivation, summary of findings, and description of the data below.

I would like to show the certain element of the data with graphical representation that will tell a story about the births during the time period. My motivation is to tell the back story of the numbers that being collected and a pattern that will be represented.

```{r}
installed.packages("crosstalk")
```


```{r}
library(tidyverse)
library(readxl)
library(dplyr)
library(ggplot2)
library(plotly)
library(crosstalk)
library(sf)
library(modeldata)

```


- Item 1

Create at least 3 appropriate visualizations based on the datasets you explore:

Include at least 1 interactive plot (make sure you save a self-contained HTML version of it as well)


```{r}
us_births_00_14 <- read_excel("data/us_births_00_14_month_name.xlsx")

us_births_00_14
```


```{r}
birth_month <- SharedData$new(us_births_00_14,
                              key = ~month_name,
                              group = 'Birth Month')
```

```{r}
birth_month %>% 
  plot_ly(x = ~year, y = ~month_name,
         hoverinfo = "text, year",
         text = ~births) %>% 
  highlight(selectize = T) 
```


- Item 2


Include at least 1 spatial visualization (make sure to include the shapefiles in the data/ subfolder)

This part of the project will be exploring the shapefiles using the data from Official State of Florida Data Portal. I am going to be looking into one of Florida county named Polk.


```{r}
loc_schools <- "C:/Users/sidan/Downloads/dataviz_mini-project_02/dataviz_mini-project_02/data/Public_Private_Schools_in_Florida-2017/gc_schools_sep17.shp"

fla_schools <- read_sf(loc_schools, quiet = TRUE)


ggplot() + geom_sf(data = fla_schools, aes(color = OP_CLASS), alpha = 0.5) 
```
focusing on the county of Polk county located in the central part of Florida State. Looking for the distribution of the school inside of this county.

I have to located the shapefile for the state of Florida located at "https://www.census.gov/geographies/mapping-files/time-series/geo/carto-boundary-file.html#:~:text=The%20cartographic%20boundary%20files%20are,new%20Cartographic%20Boundary%20File%20page."



Include at least 1 visualization of a model (for example, a linear model and its associated coefficients plot)


Scatterplots and regression lines in R

Exploring does the length of the flipper in penguins has a relationship of the bill length of the animal.

```{r}
view(penguins)
pen <- penguins
```

```{r}
ggplot(pen, aes(x = flipper_length_mm,
                     y = bill_length_mm)) +
  geom_point(size = 2,
             color = "red",
             shape = "square",
             alpha = 0.5) +
  geom_smooth(method = "lm",
              se = FALSE,
              color = "blue")
```

Going back to the original to explore other means using the scatterplot and changing the linear regression.



```{r}
ggplot(pen, aes(x = flipper_length_mm,
                     y = bill_length_mm)) +
  geom_point() +
  geom_smooth(method = "lm",
              se = FALSE)

```


```{r}
lm(bill_length_mm ~ flipper_length_mm, data = penguins)
```


```{r}
ggplot(penguins, aes(x = flipper_length_mm,
                     y = bill_length_mm,
                     colour = island)) +
  geom_point() +
  scale_color_brewer(palette = "Dark2")
```


```{r}
table(penguins$species,
      penguins$island)
```


```{r}
ggplot(penguins, aes(x = flipper_length_mm,
                     y = bill_length_mm,
                     colour = species)) +
  geom_point() +
  geom_smooth(method = "lm",
              se = FALSE) +
  scale_color_brewer(palette = "Dark2") +
  labs(x = "Flipper length",
       y = "Bill lenght",
       color = "Species",
       title = "Penguin Measurement") +
  theme_minimal()

```

```{r}

```

